Analytic Doppler Imaging

### 2019-08-06 tex/gitlinks.tex
require celerite

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/e25a0b01c116a70302de31d94e501d0c03ad9d70/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/e25a0b01c116a70302de31d94e501d0c03ad9d70/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/e25a0b01c116a70302de31d94e501d0c03ad9d70/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/7b48dcaaefaaa4a6801c5b8d446707174e057c94/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/7b48dcaaefaaa4a6801c5b8d446707174e057c94/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/7b48dcaaefaaa4a6801c5b8d446707174e057c94/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
